Report

### 2021-05-04 Rmd/report.Rmd
No idea of what I changed

```{r participants, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
# plot participants
participants %>% 
	drop_na(valid_participant) %>% 
	ggplot(aes(lp, fill = valid_participant)) +
	facet_grid(location~age_group, scales = "free") +
	geom_bar() +
	geom_hline(yintercept = 24, linetype = "dashed") +
	labs(x = "Group", y = "N", fill = "Valid?") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(axis.title.x = element_blank()) +
	ggsave(here("Figures", "sample.png"))
```

@@

attrition %>% 
	mutate(valid_trial = ifelse(valid_trial, "Valid", "Invalid"),
		   participant = paste0(participant, " (", missing_n, ", ", percent(missing_prop), ")")) %>% 
	ggplot(aes(missing, participant, colour = valid_trial)) +
	geom_point(alpha = 0.5) +
	geom_vline(xintercept = 0.25, linetype = "dashed") +
	labs(x = "Proportion of missing trials (out of 32)", y = "Participant") +
	scale_color_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(axis.text.y = element_text(colour = col, size = 8),
		  axis.title.y = element_blank(),
		  axis.text.x = element_text(colour = "black"),
		  legend.title = element_blank(),
		  legend.position = "top",
		  text = element_text(size = 15)) +
	ggsave(here("Figures", "missing.png"), height = 15)

@@

```{r gaze_time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
gaze_time %>% 
	filter(valid_participant, valid_trial) %>% 
	group_by(time_bin, trial_type, lp, age_group,location) %>% 
	summarise(
		prop = mean(prop, na.rm = TRUE),
		n = n(),
		.groups = "drop"
	) %>% 
	ungroup() %>% 
	mutate(
		se = sqrt((prop*(1-prop))/(n+4)),
		lower = prop-se,
		upper = prop+se
	) %>% 
	ggplot(aes(x = time_bin, y = prop, colour = trial_type, fill = trial_type)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_smooth() +
	#geom_line() +
	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
	geom_point(shape = 1, stroke = 1, size = 1) +
	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Condition", fill = "Condition") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(legend.title = element_blank(),
		  legend.position = "top",
		  panel.grid = element_line(colour = "grey", linetype = "dotted")) +
	ggsave(here("Figures", "gaze_time.png"))

>>>>

We collected data from `r length(unique(participants$participant))` participants, of which `r length(unique(participants$participant[participants$valid_participant]))` met the inclusion criteria and were included in data analyses. `r length(unique(participants$participant[participants$location=="Oxford"]))` were tested in Oxford, and `r length(unique(participants$participant[participants$location=="Barcelona"]))` were tested in Barcelona.

```{r participants, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}

# plot participants
participants %>% 
	drop_na(valid_participant) %>% 
	mutate(lp = ifelse(lp=="Monolingual", "Mon.", "Bil.")) %>% 
	ggplot(aes(lp, fill = valid_participant, colour = valid_participant)) +
	facet_grid(location~age_group, scales = "free") +
	geom_bar(colour = NA) +
	geom_hline(yintercept = 24, linetype = "dashed") +
	labs(x = "Group", y = "N", fill = "Valid?", colour = "Valid?") +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(axis.title.x = element_blank()) +
	ggsave(here("Figures", "sample.png"))
```

We collected data from `r sum(duplicated(participant$participant)` longitudinal participants, that is, who were tested in at least two of the three ages (21, 25, and 30). Of those, `r sum(duplicated(participant$participant[participants$location=="Oxford"])` were tested in Oxford, and `r `sum(duplicated(participants$participant[participants$location=="Barcelona"])` were tested in Barcelona.

```{r participants_cohort, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}

# plot participants
participants %>% 
	drop_na(valid_participant) %>% 
	ggplot(aes(age_group, participant, fill = valid_participant, colour = valid_participant)) +
	facet_grid(lp~location, scales = "free") +
	geom_point(size = 3, shape = 4) +
	geom_line(aes(group = participant)) +
	labs(x = "Age (months)", y = "Language profile", fill = "Valid?", colour = "Valid?") +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(axis.title.y = element_blank(),
		  axis.text.y = element_blank(),
		  axis.ticks.y = element_blank(),
		  panel.grid.major.x = element_line(colour = "grey", linetype = "dotted")) +
	ggsave(here("Figures", "sample_cohort.png"))
```

@@

attrition_summary %>% 
	mutate(valid_trial = ifelse(valid_participant, "Valid", "Invalid"),
		   participant = paste0(participant, " (", percent(missing_prop), ")")) %>% 
	ggplot(aes(missing_prop, participant, colour = valid_participant, fill = valid_participant)) +
	geom_col() +
	geom_vline(xintercept = 0.25, linetype = "dashed") +
	labs(x = "Proportion of missing trials (out of 32)", y = "Participant") +
	scale_color_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(axis.text.y = element_text(colour = col, size = 8),
		  axis.title.y = element_blank(),
		  axis.text.x = element_text(colour = "black"),
		  legend.title = element_blank(),
		  legend.position = "top",
		  text = element_text(size = 15)) +
	ggsave(here("Figures", "missing.png"), height = 15)

@@

```{r gaze_time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

lp_labels <- c("Monolingual", "Bilingual")
names(lp_labels) <- lp_labels
age_group_labels <- c("21 months", "25 months")
names(age_group_labels) <- c("21", "25")

gaze_time %>% 
	filter(valid_participant, valid_trial, age_group %in% c(21, 25),
		   location == "Barcelona") %>% 
	group_by(time_bin, trial_type, lp, age_group,location) %>% 
	summarise(
		prop = mean(prop, na.rm = TRUE),
		n = n(),
		.groups = "drop"
	) %>% 
	ungroup() %>% 
	mutate(
		se = sqrt((prop*(1-prop))/(n+4)),
		lower = prop-se,
		upper = prop+se,
		time_bin = time_bin*100
	) %>% 
	ggplot(aes(x = time_bin, y = prop, colour = trial_type, fill = trial_type)) +
	facet_grid(lp~age_group, labeller = labeller(lp = lp_labels, age_group = age_group_labels)) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_smooth() +
	#geom_line() +
	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
	geom_point(shape = 1, stroke = 1, size = 1) +
	labs(x = "Time (ms)", y = "Pr(Target fixation)", colour = "Condition", fill = "Condition") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(legend.title = element_blank(),
		  legend.position = "top",
		  panel.grid = element_line(colour = "grey", linetype = "dotted"),
		  panel.grid.minor = element_blank()) +
	ggsave(here("Figures", "gaze_time.png"), height = 5, width = 7)
